% ============================================================
% KAYNAKLAR
% Metinde geçtikleri sıraya göre numaralandırılmıştır.
% ============================================================
\begin{thebibliography}{99}
\itemsep=0pt

\bibitem{bejan_convection_2013}
A. Bejan,
\textit{Convection Heat Transfer},
4th ed., Wiley, Hoboken, NJ, 2013.

\bibitem{incropera_heat_transfer_2017}
F. P. Incropera, D. P. DeWitt, T. L. Bergman, and A. S. Lavine,
\textit{Fundamentals of Heat and Mass Transfer},
8th ed., Wiley, Hoboken, NJ, 2017.

\bibitem{pope_turbulence_2000}
S. B. Pope,
\textit{Turbulent Flows},
Cambridge University Press, Cambridge, 2000.

\bibitem{li_fno_2021}
Z. Li, N. Kovachki, K. Azizzadenesheli, B. Liu, K. Bhattacharya, A. Stuart, and A. Anandkumar,
``Fourier neural operator for parametric partial differential equations,''
in \textit{International Conference on Learning Representations (ICLR)}, 2021.

\bibitem{lu_deeponet_2021}
L. Lu, P. Jin, G. Pang, Z. Zhang, and G. E. Karniadakis,
``Learning nonlinear operators via DeepONet based on the universal approximation theorem of operators,''
\textit{Nature Machine Intelligence}, Vol.~3, No.~3, pp.~218--229, 2021.

\bibitem{raissi_pinn_2019}
M. Raissi, P. Perdikaris, and G. E. Karniadakis,
``Physics-informed neural networks: A deep learning framework for solving forward and inverse problems involving nonlinear partial differential equations,''
\textit{Journal of Computational Physics}, Vol.~378, pp.~686--707, 2019.

\bibitem{kochkov_ml_cfd_2021}
D. Kochkov, J. A. Smith, A. Alieva, Q. Wang, M. P. Brenner, and S. Hoyer,
``Machine learning--accelerated computational fluid dynamics,''
\textit{Proceedings of the National Academy of Sciences},
Vol.~118, No.~21, e2101784118, 2021.

\bibitem{krishnapriyan_failure_2021}
A. Krishnapriyan, A. Gholami, S. Zhe, R. M. Kirby, and M. W. Mahoney,
``Characterizing possible failure modes in physics-informed neural networks,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2021.

\bibitem{wang_gradient_2021}
S. Wang, Y. Teng, and P. Perdikaris,
``Understanding and mitigating gradient flow pathologies in physics-informed neural networks,''
\textit{SIAM Journal on Scientific Computing},
Vol.~43, No.~5, pp.~A3055--A3081, 2021.

\bibitem{tezgocen_bitirme1_2026}
B. Tezgöçen,
``Üç Boyutlu Taylor Green Girdabı Akışının Fizik Bilgili Sinir Ağları Kullanılarak Çözümü,''
Bitirme Çalışması, İstanbul Teknik Üniversitesi, Fen-Edebiyat Fakültesi,
Fizik Mühendisliği Bölümü, Güz 2025--2026.

\bibitem{lesnets_2024}
G. Sirignano and K. Spiliopoulos,
``LES-Nets: Large eddy simulation with neural network closures,''
\textit{arXiv preprint} arXiv:2411.04502, 2024.

\bibitem{tritton_physical_1988}
D. J. Tritton,
\textit{Physical Fluid Dynamics},
2nd ed., Oxford University Press, Oxford, 1988.

\bibitem{kolmogorov_1941}
A. N. Kolmogorov,
``The local structure of turbulence in incompressible viscous fluid for very large Reynolds numbers,''
\textit{Doklady Akademii Nauk SSSR}, Vol.~30, No.~4, pp.~301--305, 1941.

\bibitem{smagorinsky_1963}
J. Smagorinsky,
``General circulation experiments with the primitive equations: I. The basic experiment,''
\textit{Monthly Weather Review}, Vol.~91, No.~3, pp.~99--164, 1963.

\bibitem{kays_turbulent_prandtl_1994}
W. M. Kays,
``Turbulent Prandtl number---where are we?,''
\textit{ASME Journal of Heat Transfer}, Vol.~116, No.~2, pp.~284--295, 1994.

\bibitem{calzavarini_damping_2014}
E. Calzavarini, F. Toschi, and R. Tripiccione,
``Evidences of Bolgiano--Obukhov scaling in three-dimensional Rayleigh--B\'enard convection,''
\textit{Physical Review E}, Vol.~89, 023019, 2014.

\bibitem{morinishi_skew_1998}
Y. Morinishi, T. S. Lund, O. V. Vasilyev, and P. Moin,
``Fully conservative higher order finite difference schemes for incompressible flow,''
\textit{Journal of Computational Physics}, Vol.~143, No.~1, pp.~90--124, 1998.

\bibitem{boffetta_ecke_2012}
G. Boffetta and R. E. Ecke,
``Two-dimensional turbulence,''
\textit{Annual Review of Fluid Mechanics}, Vol.~44, pp.~427--451, 2012.

\bibitem{kingma_adam_2015}
D. P. Kingma and J. Ba,
``Adam: A method for stochastic optimization,''
in \textit{International Conference on Learning Representations (ICLR)}, 2015.

\bibitem{loshchilov_sgdr_2017}
I. Loshchilov and F. Hutter,
``SGDR: Stochastic gradient descent with warm restarts,''
in \textit{International Conference on Learning Representations (ICLR)}, 2017.

\bibitem{paszke_pytorch_2019}
A. Paszke et al.,
``PyTorch: An imperative style, high-performance deep learning library,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2019.

\end{thebibliography}
